---
author: "Mahesh Reddy"
output:
  html_document:
    number_sections: false
    toc: true
    toc_depth: 6
    highlight: tango
    theme: cosmo
    smart: true
    df_print: paged
editor_options:
  chunk_output_type: console
---






```{r echo=FALSE,message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
set.seed(123)
# Data manipulation
if(!require(summarytools)){
    install.packages("summarytools")
    library(summarytools)
}
if(!require(xtable)){
    install.packages("xtable")
    library(xtable)
}
if(!require(tm)){
    install.packages("tm")
    library(tm)
}
if(!require(wordcloud)){
    install.packages("wordcloud")
    library(wordcloud)
}
if(!require(plotly)){
    install.packages("plotly")
    library(plotly)
}
if(!require(purrr)){
    install.packages("purrr")
    library(purrr)
}
if(!require(stringr)){
    install.packages("stringr")
    library(stringr)
}
if(!require(IRdisplay)){
    install.packages("IRdisplay")
    library(IRdisplay)
}
if(!require(repr)){
    install.packages("repr")
    library(repr)
}

if(!require(data.table)){
    install.packages("data.table")
    library(data.table)
}
if(!require(magrittr)){
    install.packages("magrittr")
    library(magrittr)
}
if(!require(qwraps2)){
    install.packages("qwraps2")
    library(qwraps2)
}
if(!require(dplyr)){
    install.packages("dplyr")
    library(dplyr)
}

if(!require(DT)){
    install.packages("DT")
    library(DT)
}

# Time manipulation
if(!require(lubridate)){
    install.packages("lubridate")
    library(lubridate)
}

# Visualization
if(!require(ggplot2)){
    install.packages("ggplot2")
    library(ggplot2)
}

if(!require(plotrix)){
    install.packages("plotrix")
    library(plotrix)
}

if(!require(corrplot)){
    install.packages("corrplot")
    library(corrplot)
}

if(!require(ggdendro)){
    install.packages("ggdendro")
    library(ggdendro)
}

if(!require(ggrepel)){
    install.packages("ggrepel")
    library(ggrepel)
}
# Text manipulation
if(!require(tidytext)){
    install.packages("tidytext")
    library(tidytext)
}

if(!require(stringr)){
    install.packages("stringr")
    library(stringr)
}

if(!require(tm)){
    install.packages("tm")
    library(tm)
}

if(!require(sentimentr)){
    install.packages("sentimentr")
    library(sentimentr)
}

if(!require(wordcloud)){
    install.packages("wordcloud")
    library(wordcloud)
}

if(!require(RSentiment)){
    install.packages("RSentiment")
    library(RSentiment)
}


if(!require(RSentiment)){
    install.packages("RSentiment")
    library(RSentiment)
}
if(!require(corrgram)){
    install.packages("corrgram")
    library(corrgram)
}
if(!require(hexbin)){
    install.packages("hexbin")
    library(hexbin)
}

if(!require(GGally)){
    install.packages("GGally")
    library(GGally)
}
if(!require(gridExtra)){
    install.packages("gridExtra")
    library(gridExtra)
}
if(!require(jsonlite)){
    install.packages("jsonlite")
    library(jsonlite)
}
    
```



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
x = read_json("FR_category_id.json", simplifyVector = FALSE)
ht <- new.env()
for(x in x$items){
    assign(as.character(x$id), x$snippet$title, ht)
    }
fr <- read.csv("FRvideos.csv", header = TRUE, sep = ",", quote = "\"",
        dec = ".", fill = TRUE, comment.char = "")
getCategory <- function(id){
    tryCatch({
    get(as.character(id), ht)
}, error = function(e) {
    'undefined'
})
             }

videos <- as.data.table(fr)
videos$trending_date <- ydm(videos$trending_date)
videos$publish_time <- ymd(substr(videos$publish_time,start = 1,stop = 10))
dif_days = lapply((videos$trending_date-videos$publish_time), as.numeric)
videos$dif_days <- as.numeric(unlist(dif_days)) #Actually dif_day is a time difference in day, 
#we apply a function that convert time difference in day in double type
videos[,"Percentage_Likes":=round(100*(likes)/views,digits = 4)]
videos[,"Percentage_Disikes":=round(100*(dislikes)/views,digits = 4)]
videos[,"Percentage_comments":=round(100*(comment_count)/views,digits = 4)]
videos[,"Percentage_views_days":=round(100*(views)/dif_days,digits = 4)]
videos[,"Links_count":= str_count(description, pattern = "http")]
url_pattern <- "http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\\(\\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+"
videos$description <- flatten_chr(map(videos$description, function(x) str_replace_all(x, "\\\\n|,", " ")))
videos[,"Urls_description":= str_extract_all(description, pattern = url_pattern)]
videos[,"Reference_count":= str_count(Urls_description, pattern = "www.youtube.com/channel|www.youtube.com/user/")]
videos$category <- flatten_chr(map(videos$category_id,function(x) getCategory(x)))
videos = videos[order(views, decreasing=TRUE)]

```



```{r echo=FALSE}
p <- plot_ly(videos, labels = ~category, type = 'pie') %>%
  layout(title = 'Number of videos per category',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```

```{r echo=FALSE}
p <- plot_ly(videos, labels = ~category, values = ~views, type = 'pie') %>%
  layout(title = 'Youtubes Video Views per categories',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```



# Relationship betwenn Views, Likes and Coment Counts 
```{r echo=FALSE}
colors <- c('#4AC6B7', '#1972A4', '#965F8A', '#FF7070', '#C61951')
p = plot_ly(x=videos$likes, y=videos$views, z=videos$comment_count, marker = list(color = videos$views, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Likes'),
                     yaxis = list(title = 'Views'),
                     zaxis = list(title = 'Comment Counts')))
p
```






# Analysis of title & tags with wordcloud
Word analysis gives us a good idea of the themes of the moment, the types of videos that work by categories.
We therefore retrieve a set of words that returns frequently by removing as many linking words as possible and we can return a bag of words associated with the category and the text

## Word cloud of videos title per categories {.tabset .tabset-fade}

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

#Testing a bug
freqWord = function(categ) {
docs = Corpus(VectorSource(videos[category == categ]$title))

toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("des", "les", "pas", "de", "est", "plus", "vos")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
# docs <- tm_map(docs, stemDocument)
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
}
```

### Music 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
freqWord("Music")
```


### Entertainment

```{r echo=FALSE ,message=FALSE, warning=FALSE}
freqWord("Entertainment")
```


### Gaming

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Gaming")
```

### Film & Animation

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Film & Animation")
```

### Autos & Vehicles

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Autos & Vehicles")
```

### Pets & Animals

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Pets & Animals")
```

### Sports

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Sports")
```

### Travel & Events

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Travel & Events")
```

### Gaming

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Gaming")
```

### People & Blogs

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("People & Blogs")
```

### Comedy

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Comedy")
```

### News & Politics

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("News & Politics")
```

### Howto & Style

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Howto & Style")
```

### Education

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Education")
```

### Science & Technology

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("Science & Technology")
```

### Undefined

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWord("undefined")
```



## Word cloud of of videos tags per categories {.tabset .tabset-fade}

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
freqWordTag = function(categ) {
docs = Corpus(VectorSource(videos[category == categ]$tags))

toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("des", "les", "pas", "de", "est", "plus", "vos", "none")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
# docs <- tm_map(docs, stemDocument)
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
}
```

### Music 

```{r echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
freqWordTag("Music")
```


### Entertainment

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Entertainment")
```


### Gaming

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Gaming")
```

### Film & Animation

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Film & Animation")
```

### Autos & Vehicles

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Autos & Vehicles")
```

### Pets & Animals

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Pets & Animals")
```

### Sports

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Sports")
```

### Travel & Events

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Travel & Events")
```

### Gaming

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Gaming")
```

### People & Blogs

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("People & Blogs")
```

### Comedy

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Comedy")
```

### News & Politics

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("News & Politics")
```

### Howto & Style

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Howto & Style")
```

### Education

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Education")
```

### Science & Technology

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("Science & Technology")
```

### Undefined

```{r echo=FALSE, message=FALSE, warning=FALSE}
freqWordTag("undefined")
```

## Analysis 1% / 10% / 25% of views {.tabset .tabset-fade}
The goal of this study is to determine how the views field of the videos behave when we compare the top 1% , 10%, 25% vs the rest.

```{r echo=FALSE}
subset = function(percentage) {
    len = length(videos$likes)
   return (list((left = videos[0:floor(len*percentage)]), (right = videos[floor((len*percentage)+1): len-1])))
}
```

### 25% / 75%

```{r echo=FALSE, message=FALSE, warning=FALSE}
x = subset(0.25)
left = x[[1]]
right = x[[2]]
left = left[category != 'Music']
right = right[category != 'Music']
p1 <- plot_ly(type = 'box')  %>%
  add_boxplot(x = left$category, y = left$views, 
              name = "Views 25%", boxpoints = 'outliers',
              marker = list(color = 'rgb(107,174,214)'),
              line = list(color = 'rgb(107,174,214)')) %>%
  layout(p, yaxis = list(type = "log"))
p2 <- plot_ly(type = 'box')  %>%
  add_boxplot(x = right$category, y = right$views, name = "Views 75%", boxpoints = 'outliers',
              marker = list(color = 'rgb(9,56,125)'),
              line = list(color = 'rgb(9,56,125)'))%>%
  layout(p, yaxis = list(type = "log"), title = "Box plots for views for 2 subdataset")
p <- subplot(p1, p2)
p
```

### 10% / 90%

```{r echo=FALSE, message=FALSE, warning=FALSE}
x = subset(0.10)
left = x[[1]]
right = x[[2]]
left = left[category != 'Music']
right = right[category != 'Music']
p1 <- plot_ly(type = 'box')  %>%
  add_boxplot(x = left$category, y = left$views, 
              name = "Views 10%", boxpoints = 'outliers',
              marker = list(color = 'rgb(107,174,214)'),
              line = list(color = 'rgb(107,174,214)')) %>%
  layout(p, yaxis = list(type = "log"))
p2 <- plot_ly(type = 'box')  %>%
  add_boxplot(x = right$category, y = right$views, name = "Views 90%", boxpoints = 'outliers',
              marker = list(color = 'rgb(9,56,125)'),
              line = list(color = 'rgb(9,56,125)'))%>%
  layout(p, yaxis = list(type = "log"), title = "Box plots for views for 2 subdataset")
p <- subplot(p1, p2)
p
```

### 1% / 99%

```{r echo=FALSE, message=FALSE, warning=FALSE}
x = subset(0.1)
left = x[[1]]
right = x[[2]]
left = left[category != 'Music']
right = right[category != 'Music']
p1 <- plot_ly(type = 'box')  %>%
  add_boxplot(x = left$category, y = left$views, 
              name = "Views 1%", boxpoints = 'outliers',
              marker = list(color = 'rgb(107,174,214)'),
              line = list(color = 'rgb(107,174,214)')) %>%
  layout(p, yaxis = list(type = "log"))
p2 <- plot_ly(type = 'box')  %>%
  add_boxplot(x = right$category, y = right$views, name = "Views 99", boxpoints = 'outliers',
              marker = list(color = 'rgb(9,56,125)'),
              line = list(color = 'rgb(9,56,125)'))%>%
  layout(p, yaxis = list(type = "log"), title = "Box plots for views for 2 subdataset")
p <- subplot(p1, p2)
p
```


